---
title: "earthquakes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{earthquakes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(earthquakes)
```

# Earthquakes visulaization

## Introduction

This package allows one to visualize the NOAA significant earthquake data
in various ways.

## Loading and cleaning the data

You can load the NOAA earthquake data using the load_data function. Then
use the eq_clean_data function to prepare a cleaned up data set. This creates
a proper DATE column, cleans up the LOCATION column and fixes various data
types.

```{r}
data <- load_data()
data <- eq_clean_data(data)
tibble::glimpse(data)
```

## Cleaning the location

The eq_clean_data function also cleans the LOCATION column. This is done
by calling the eq_location_clean function.

```{r}
location <- c("ABC", "ABC: DEF", "ABC: DEF: GHI")
eq_location_clean(location)
```

## Plotting a timeline

The earthquakes can be plotted on a timeline, including optional labels.

```{r}
data <- eq_clean_data(load_data())
data <- data[data$COUNTRY %in% c("GREECE", "TURKEY") & data$YEAR > 2005, ]
ggplot2::ggplot(data) +
  geom_timeline(ggplot2::aes(x = DATE, y = COUNTRY)) +
  geom_timeline_label(ggplot2::aes(x = DATE, y = COUNTRY, label = LOCATION_NAME))
```

## Plotting a leaflet map

The earthquakes can be plotted on a map, including interactive labels.

```{r}
data <- eq_clean_data(load_data())
data <- data[data$COUNTRY %in% c("GREECE", "TURKEY") & data$YEAR > 2005, ]
data$LABEL <- eq_create_label(data)
eq_map(data, annot_col = "LABEL")
```

